\chapter*{Abstract}

Electroencephalography (EEG) is a cornerstone tool in clinical and experimental neuroscience, yet it frequently suffers from channel loss due to contact failures, motion artifacts, or amplifier saturation. Interpolating these missing channels is a critical preprocessing step, traditionally addressed through geometric methods such as spherical splines, implemented in reference libraries like MNE-Python. However, these methods operate exclusively in the spatial domain, ignoring the brain's true functional connectivity and the temporal dynamics of the signals.

This thesis presents a reproducible and exhaustive benchmark comparing eighteen EEG channel interpolation methods —geometric, statistical, and Graph Signal Processing (GSP)-based— under a rigorous experimental protocol. The design encompasses three heterogeneous databases (64-channel PhysioNet, 22-channel BCI Competition IV 2a, and 60-channel MNE Sample), 120 loss scenarios combining random and contiguous modes at severities from 10\% to 40\%, and a battery of six metrics covering amplitude error (MAE, RMSE, SNR), morphological fidelity (DTW), and spectral preservation (LSD, Coherence). To ensure a fair comparison, all methods —including classical baselines— were optimized via Optuna with over 15,000 parametric configurations explored, and a confirmatory validation against MNE-Python's industrial implementation was incorporated.

Results reveal that temporal regularization is a decisive turning point: TRSS-family methods (\textit{Temporal Regularized Sobolev Smoothness}) consistently outperform geometric baselines and purely spatial GSP methods, with gains of 5 to 10~dB in SNR under severe contiguous loss (40\%). Analysis of the underlying mechanism shows this advantage stems not from better spatial representation, but from the temporal continuity constraint acting as a complementary physiological prior. Nevertheless, under favorable regimes (dense montages, random loss at or below 20\%), MNE-Python matches or surpasses TRSS in spectral preservation while being 50 to 100 times faster. We conclude that TRSS is the preferred method when morphological preservation under severe loss is paramount, whereas MNE remains the optimal choice for settings with moderate loss and real-time constraints.

All code, experimental configurations, optimization logs, and result artifacts are available in an open repository ensuring full reproducibility of the findings.

\vspace{1em}
\noindent\textbf{Keywords:} EEG, missing channels, interpolation, Graph Signal Processing (GSP), temporal regularization, TRSS, spherical splines, MNE-Python, Bayesian optimization, Optuna, reproducible benchmark.