\section{Conclusion}

This paper's primary contribution is methodological: we establish a unified, reproducible, and fair benchmark for EEG interpolation methods. By subjecting all algorithms—including classical baselines—to rigorous hyperparameter optimization via Optuna, we demonstrate that the performance gap between traditional and modern methods is substantially smaller than typically reported in the literature. This is not a weakness but rather a strength: it clarifies that realistic performance requires careful tuning, not algorithmic novelty alone.

Within this fair evaluation framework, a clear empirical finding emerges: temporal regularization methods, particularly TRSS, achieve competitive reconstruction quality with average MAE of \ResTVMAE\ and SNR of \ResTVSNR~dB, outperforming exhaustively optimized geometric baselines such as Spherical Spline (MAE $\approx$ \ResBaselineMAE, SNR $\approx$ \ResBaselineSNR~dB).

Beyond standard error metrics, TRSS and Tikhonov regularization demonstrate robust superiority in physiological fidelity. TRSS preserves signal dynamics (DTW $\approx$ \ResTVDTW), minimizes phase distortion, and accurately recovers Event-Related Potentials (ERP) and Power Spectral Density (PSD) even under severe contiguous channel loss (e.g., 40\% nearby missing channels). This supports the conclusion that incorporating temporal smoothness priors into the spatial graph Laplacian framework provides an advantage over purely spatial models.

\subsection*{Trial-Level Statistical Validation}
A comprehensive trial-level pairwise analysis across 736 iterations and 4,336 aggregated samples confirms the statistical robustness of these conclusions. Using the Mann-Whitney U test with Cliff's delta effect size, we conducted 55 pairwise method comparisons after excluding the visibility-based outlier from the ranking. The results demonstrate strong statistical significance: 39 comparisons achieved $p < 0.05$, and 38 reached $p < 0.001$. Temporal and spatial-temporal methods (temporal\_laplacian, TRSS, IDW, linear) clustered tightly in the top tier (median MAE: 0.075--0.081) with no statistically significant separation. This trial-level confirmation validates the iteration-level findings and establishes a clear performance hierarchy robust across diverse experimental contexts.

The extensive validation across PhysioNet, BCI Competition IV 2a, and MNE Sample datasets confirms the generalizability of these findings. This work provides a reference point for future EEG interpolation research, emphasizing the importance of fair benchmarking and rigorous hyperparameter optimization. Future work should explore whether real-time performance can be achieved through GPU acceleration or approximation strategies, and whether task-specific or subject-specific tuning yields additional performance gains.
