\section{Discussion}

The comprehensive hyperparameter optimization conducted via the Optuna framework, across multiple disparate datasets, provides a robust confirmation of the working hypothesis. The results suggest a paradigm shift in EEG interpolation: graph-aware and temporal-regularization (TV) methods are not merely theoretically competitive, but practically superior in realistic missing-channel scenarios when properly tuned.

\subsection{Physiological and Temporal Fidelity (ERP \& PSD)}
A critical finding from the optimization phase is the profound impact of temporal regularization on physiological signal features. Even when geometric baselines (e.g., Spherical Spline or RBFI) are exhaustively optimized to minimize their spatial error, they fundamentally operate as spatial smoothers. In contrast, TRSS incorporates prior knowledge of the temporal smoothness inherent in neuroelectric generators. 

This advantage is most evident in the preservation of Event-Related Potentials (ERPs) and Power Spectral Density (PSD). As shown previously in the Results section (\figurename~\ref{fig:erp_optimized} and \figurename~\ref{fig:psd_optimized}), TRSS accurately recovers the amplitude and latency of ERP components (such as the P300 or N100) even under severe contiguous channel loss (40\% nearby missing channels). Baselines optimized for spatial "best cases" suffer from phase distortion and amplitude attenuation in the time domain, compromising subsequent clinical or BCI downstream tasks.

\subsection{Multi-Dataset Generalization}
The variance in performance across datasets underscores the importance of the Optuna optimization framework. In densely sampled, highly correlated configurations (PhysioNet, 64 channels), spatial models perform adequately. However, in lower-density setups or those with complex temporal dynamics (BCI IV 2a and MNE Sample), the temporal priors of TRSS provide a substantial buffer against catastrophic failure, particularly when nearby clusters of electrodes are lost. 

\subsection{Positioning Against Deep Learning Approaches}
It is important to contextualize these results against the broader landscape of EEG reconstruction methods. Recent deep learning approaches---including convolutional autoencoders, graph neural networks (GNNs), and transformer-based architectures---have shown promise in related signal imputation tasks. However, a direct comparison was intentionally excluded from this benchmark for two principled reasons. First, GSP methods like TRSS are \emph{training-free}: they require no pre-training phase, no labeled data, and no subject-specific calibration, making them immediately deployable on any EEG montage. Second, the theoretical convergence of the TRSS gradient descent is guaranteed by the Lipschitz bound (Eq.~\ref{eq:lipschitz}), providing interpretability and reliability that black-box neural networks cannot offer. Future work should investigate hybrid architectures that combine the inductive biases of GSP with the representational power of learned models.

\subsection{Limitations}
\subsubsection{Computational Cost and Deployment}
TRSS is not the lowest-latency option in the benchmark. Because it optimizes a full signal window with iterative gradient descent, its cost grows with the number of channels, the number of time samples, and the number of iterations. In the companion thesis microbenchmark, TRSS measured 9.44~ms per call on a $50\times64$ fixture with 10\% missing entries, which is slower than single-pass interpolators such as linear, mean, and IDW, yet far faster than the heaviest iterative methods in the same fixture. This supports an interpretation of TRSS as a high-fidelity method whose real-time suitability still depends on hardware acceleration and deployment constraints.

This study has limitations that should be acknowledged. First, the missing-channel simulation uses binary masking (channel fully present or absent), whereas real degradation is often gradual. Second, all datasets correspond to healthy adult subjects; validation on clinical populations (epilepsy, neonates) remains an open question. Third, the current evaluation uses a single temporal split per dataset; future work could employ $k$-fold temporal cross-validation for tighter confidence bounds.

\subsection{Robustness to Fixed Hyperparameters}
A natural concern with per-scenario optimization is whether TRSS performance is fragile to the specific $\alpha, \beta$ values found for each degradation level. To address this, we evaluated TRSS using a single \emph{global} set of hyperparameters per dataset (the median of all per-scenario optima). Across all 42 experimental contexts, the global configuration exhibited a mean MAE change of $-0.7\%$ (i.e., negligibly \emph{better} than per-scenario tuning, due to the robustness of the median) and a mean SNR loss of only $0.46$~dB. These results demonstrate that TRSS is inherently robust to the choice of regularization parameters and does not require re-optimization for each specific failure pattern---a critical property for real-world BCI deployment where degradation is unpredictable.

\subsection{Concluding Remarks on Fair Benchmarking}
Historically, novel algorithms are often compared against default-configured baselines, inflating perceived improvements. By subjecting all methods---including classical splines---to rigorous, dataset-specific hyperparameter search, this study establishes a fair and demanding evaluation standard. The fact that TRSS and Tikhonov regularization maintain statistically significant margins (Bonferroni-corrected $p < 0.001$) over optimized baselines validates the fundamental premise: integrating spatial graph topology with temporal smoothness priors constitutes a structurally superior framework for EEG signal recovery.
