\section{Introduction}

Electroencephalography (EEG) recordings frequently exhibit missing channels due to contact issues, amplifier saturation, movement artifacts, or quality-control rejection. In practical studies, this is not a minor inconvenience: missing channels can distort spatial interpretations, degrade clinical biomarkers like Event-Related Potentials (ERPs), and reduce the reliability of downstream Brain-Computer Interface (BCI) decoding pipelines. Because of that, channel interpolation has been studied for decades, from classical spatial interpolation to graph-based reconstruction.

Graph Signal Processing (GSP) provides a natural framework for this problem by representing electrodes as graph vertices and modeling inter-channel relationships through weighted edges. The general perspective is consistent with the graph-signal literature associated with Ortega and collaborators \cite{shuman2013,ortega2018}, where smoothness, bandlimitedness, and spectral structure are used to replace purely geometric interpolation with graph-constrained estimation.

Even though many methods have been proposed in the literature \cite{narang2013,puy2018,zhang2024bgsrp}, in practice it is still difficult to compare them fairly. Different papers use different masks, datasets, and evaluation conventions, and frequently evaluate novel methods against unoptimized baseline configurations, inflating performance claims. This study aims to reduce that gap with a unified benchmark and rigorous hyperparameter optimization.

Recent advances in deep learning have also been applied to EEG reconstruction, including convolutional autoencoders \cite{banville2021uncovering}, graph neural networks \cite{defferrard2016}, and transformer architectures. While these data-driven approaches can achieve competitive performance, they require large labeled training datasets, are prone to domain shift across subjects and recording setups, and lack the theoretical convergence guarantees offered by model-based optimization. In contrast, GSP methods such as TRSS are \emph{training-free}: they operate directly on the test signal using only the electrode topology and physically motivated smoothness priors, making them immediately applicable to any EEG montage without prior training. This fundamental distinction motivates our focus on model-based methods in this work, while acknowledging deep learning as a complementary and promising research direction.

The main contributions of this manuscript are:
\begin{itemize}
\item A unified and reproducible pipeline that covers graph construction, missing-channel simulation, reconstruction, and quantitative evaluation across multiple datasets (PhysioNet, BCI Competition IV 2a, and MNE Sample).
\item A cross-family comparison including geometric baselines (Spherical Spline, TPS), independent component analysis (ICA), and advanced graph-based interpolation with temporal regularization (TRSS, Tikhonov).
\item Extensive hyperparameter optimization using the Optuna framework to fairly benchmark all methods---including classical baselines---under varying conditions (nearby vs. random missing channels).
\item A physiological analysis demonstrating the superiority of temporal regularization in preserving Event-Related Potentials (ERPs) and Power Spectral Density (PSD) dynamics under severe channel loss.
\end{itemize}

We comprehensively evaluate performance using six metrics (MAE, RMSE, SNR, DTW, LSD, and Coherence) under \ResScenariosNamesEn~scenario-driven masking conditions (spanning proportional ratios and discrete channel counts) with repeated runs and consolidated variability statistics.

This manuscript's primary contribution is methodological: we establish a unified, reproducible, and fair benchmarking framework for EEG interpolation. Rather than proposing a fundamentally novel algorithm, we demonstrate that \emph{rigorous hyperparameter optimization} substantially closes the gap between classical baselines and modern methods. Under this fair evaluation, temporal regularization methods like TRSS perform competitively, with particular strength in preserving physiological dynamics (ERPs, spectral content) under severe channel loss. This work serves as a reference point for future research, showing both the promise and the realistic performance ceiling of each method class.
