\section{Methods}

We represent EEG channels as graph vertices and model inter-channel relationships with weighted adjacency matrices. Let $\mathcal{G} = (\mathcal{V}, \mathcal{E}, \mathbf{W})$ be an undirected weighted graph where $\mathcal{V}$ is the set of $N$ electrode vertices, $\mathcal{E}$ the edge set, and $\mathbf{W} \in \mathbb{R}^{N \times N}$ the symmetric weight matrix. The combinatorial graph Laplacian is $\mathbf{L} = \mathbf{D} - \mathbf{W}$, where $\mathbf{D}$ is the degree matrix defined as $D_{ii} = \sum_j W_{ij}$. A graph signal $\mathbf{x} \in \mathbb{R}^{N}$ assigns a scalar value (e.g., electrical potential) to each electrode at a given time instant.

The goal is to formally compare geometric interpolation baselines against advanced Graph Signal Processing (GSP) methods incorporating temporal regularization under exactly the same rigorously optimized experimental conditions.

\subsection{Graph Construction}
The foundation of any GSP approach is the underlying topology. We evaluate several graph constructors organized into three categories:
\begin{itemize}
\item \emph{Neighborhood graphs}: $k$-NN (\iterid{knn}), Gaussian-weighted $k$-NN (\iterid{knng}), variable-$k$ NN (\iterid{vknng}), epsilon-ball (\iterid{epsilon_ball}), and minimum spanning tree (\iterid{mst}). The Gaussian-weighted $k$-NN defines edge weights as $W_{ij} = \exp(-d(i,j)^2 / \sigma^2)$ for the $k$ nearest neighbors based on Euclidean distance $d(i,j)$ between 3D electrode coordinates.
\item \emph{Dense/global graphs}: fully connected inverse-distance (\iterid{fully_connected_inverse_distance}) and Gaussian kernel (\iterid{gaussian}).
\item \emph{Adaptive/learned graphs}: non-negative kernel regression \cite{shekkizhar2020} (\iterid{nnk}), adaptive edge weighting \cite{kalofolias2016} (\iterid{aew}), and graph learning via log-degree regularization \cite{kalofolias2016} (\iterid{kalofolias}).
\end{itemize}

For the final benchmarking, we utilized Gaussian-weighted $k$-NN (\iterid{knng}) due to its numerical stability, computational efficiency, and empirical superiority in capturing local spatial correlations among scalp electrodes.

\subsection{Interpolation Families}

Let $\mathcal{K}$ denote the set of known (observed) channels and $\mathcal{U}$ the unknown (missing) channels. We compare three distinct families of methods:

\paragraph{Geometric/Spline Baselines} 
Classical alternatives that do not exploit graph theory, relying strictly on Euclidean distance or surface projections. The most prominent baseline in EEG research is the \emph{Spherical Spline} \cite{perrin1989}. It models the scalp potential as a function $V(\mathbf{r}) = c_0 + \sum_{i \in \mathcal{K}} c_i \, g(\mathbf{r}, \mathbf{r}_i)$, where $\mathbf{r}_i$ are electrode coordinates, and $g(\mathbf{r}, \mathbf{r}_i) = \frac{1}{4\pi} \sum_{n=1}^{\infty} \frac{2n+1}{n^m (n+1)^m} P_n(\cos(\theta))$ using Legendre polynomials $P_n$ and the angle $\theta$ between vectors. While geometrically elegant, it operates strictly in the spatial domain for every individual time sample, completely ignoring temporal continuity.

\paragraph{Instant GSP Methods (Tikhonov)} 
These methods operate independently at each time sample using graph priors. The graph Laplacian regularization problem, also known as Tikhonov regularization on graphs, enforces spatial smoothness:
\begin{equation}
  \hat{\mathbf{x}}_{\mathcal{U}} = \arg\min_{\mathbf{z}}
    \|\mathbf{z} - \mathbf{x}_{\mathcal{K}}\|^2 + \alpha \, \mathbf{z}^\top \mathbf{L}_{\mathcal{U}\mathcal{U}} \mathbf{z},
  \label{eq:tikhonov}
\end{equation}
where $\alpha$ controls the smoothness penalty. The pure GSP case (hard constraint) corresponds to the limit $\alpha \to \infty$, yielding the closed-form solution $\hat{\mathbf{x}}_{\mathcal{U}} = -\mathbf{L}_{\mathcal{U}\mathcal{U}}^{-1} \mathbf{L}_{\mathcal{U}\mathcal{K}} \mathbf{x}_{\mathcal{K}}$. 

\paragraph{Temporal Regularization Methods (TRSS)} 
These methods jointly optimize spatial and temporal criteria over an entire signal matrix (or epoch) $\mathbf{X} \in \mathbb{R}^{N \times T}$. The Temporal Regularized Sobolev Smoothness (TRSS) method \cite{giraldo2022} explicitly penalizes high-frequency variations in both the graph domain and the time domain:
\begin{equation}
  \hat{\mathbf{X}} = \arg\min_{\mathbf{Z}}
    \|\mathbf{Z}_{\mathcal{K},:} - \mathbf{X}_{\mathcal{K},:}\|_F^2
    + \alpha \operatorname{tr}(\mathbf{Z}^\top \mathbf{L} \mathbf{Z})
    + \beta \|\Delta_t \mathbf{Z}\|_F^2,
  \label{eq:sobolev}
\end{equation}
where $\|\cdot\|_F$ is the Frobenius norm, $\operatorname{tr}(\cdot)$ is the trace operator, and $\Delta_t$ is a finite-difference operator along the time axis. The hyperparameter $\beta$ explicitly controls the assumption of temporal smoothness, mirroring the low-frequency physiological nature of most EEG signals.

\subsection{Evaluation Metrics}

Performance is assessed with six complementary metrics:
\begin{itemize}
\item \textbf{Mean Absolute Error (MAE)} and \textbf{Root Mean Square Error (RMSE)}: Capture pointwise amplitude accuracy. RMSE heavily penalizes large local deviations, serving as a proxy for outlier generation.
\item \textbf{Dynamic Time Warping (DTW)}: Evaluates temporal morphological fidelity. Unlike Euclidean distance, DTW is robust to slight phase shifts, making it ideal for assessing Event-Related Potentials (ERP).
\item \textbf{Signal-to-Noise Ratio (SNR)}: Provides a global quality view, bounded and easily interpretable across different sensor scales.
\item \textbf{Log Spectral Distance (LSD)}: Evaluates the logarithmic distance between the Power Spectral Density (PSD) of the reconstructed signal and the original signal, quantifying the preservation of the frequency content across critical physiological bands.
\item \textbf{Magnitude-Squared Coherence}: Quantifies the frequency-domain correlation and phase consistency between the reconstructed signal and the original true signal.
\end{itemize}

This six-metric combination is essential in EEG: A method with low MAE may still distort temporal dynamics (destroying ERPs), and a method competitive on DTW might fail to preserve spectral coherence.

\subsection{Hyperparameter Optimization (Optuna)}

A crucial aspect of our methodology is ensuring a fair and rigorous comparison between families. Advanced methods like TRSS depend heavily on hyperparameters (e.g., temporal weight $\beta$, spatial weight $\alpha$, and graph sparsity $k$). However, geometric baselines (like splines) also possess tunable parameters (e.g., polynomial stiffness $m$).

To prevent the pervasive literature bias of comparing finely-tuned novel algorithms against default-configured baselines, we utilized the Optuna framework \cite{akiba2019optuna}. We defined a systematic search space for each algorithm:
\begin{itemize}
\item \textbf{TRSS}: $\alpha \in [10^{-3}, 10^{2}]$ (log scale), $\beta \in [10^{-3}, 10^{2}]$ (log scale), $k \in [3, 20]$.
\item \textbf{Tikhonov}: $\alpha \in [10^{-3}, 10^{2}]$ (log scale), $k \in [3, 20]$.
\item \textbf{Spherical Splines / RBF}: stiffness/smoothness parameters tuned extensively across continuous ranges.
\end{itemize}
Optimization was executed using the Tree-structured Parzen Estimator (TPE) algorithm, targeting the minimization of MAE over $100$ trials for every specific dataset and missing-channel scenario combination.
