\section{Related Work}

\subsection{Classical EEG Interpolation}
The problem of interpolating missing EEG channels has historically been addressed using geometric and statistical methods. The most widely adopted baseline is the Spherical Spline interpolation \cite{perrin1989}, which models the scalp as a continuous sphere and projects observed potentials to missing electrode locations using distance-weighted polynomials. Other variants include Radial Basis Function Interpolation (RBFI) \cite{jager2016} and Thin-Plate Splines. While these methods are computationally inexpensive and simple to implement, they operate strictly in the spatial domain for isolated time samples. They inherently assume that electrical potentials vary smoothly across the scalp's surface but completely ignore the underlying functional connectivity and the temporal continuity of the neurophysiological generators.

As an alternative, statistical methods such as Independent Component Analysis (ICA) attempt to project the data into a set of independent sources, reconstruct the missing sensors from the source signals, and project back to the sensor space. However, ICA struggles with non-stationary artifacts and often suppresses localized high-frequency bursts when reconstructing missing channels.

\subsection{Graph Signal Processing (GSP)}
Graph-based interpolation for missing data in structured signals represents a significant shift from purely Euclidean distance metrics. Early formulations by Narang and Ortega \cite{narang2013} demonstrated that interpolation can be cast as an optimization problem where signals are constrained to be smooth with respect to a graph topology. Further theoretical work by Puy \emph{et al.} \cite{puy2018} clarified the conditions under which bandlimited graph signals can be accurately recovered from partial observations.

The overarching GSP framework, as comprehensively detailed by Shuman \emph{et al.} \cite{shuman2013} and Ortega \emph{et al.} \cite{ortega2018}, establishes the intuition that a graph Laplacian can replace the traditional spatial derivative operator when data resides on an irregular manifold, such as the human scalp. More recent methods have expanded on this by integrating Reproducing Kernel Hilbert Spaces (RKHS) for continuous recovery, such as the BGSRP algorithm \cite{zhang2024bgsrp}.

\subsection{Temporal Regularization and the Benchmarking Gap}
While static GSP methods successfully incorporate spatial topology, they still reconstruct signals frame-by-frame. Recent advancements in time-varying graph signals \cite{giraldo2022} address this by introducing Sobolev smoothness constraints across the time axis, jointly optimizing both spatial and temporal derivatives. 

Despite the proliferation of these advanced algorithms, the literature suffers from a substantial benchmarking gap. Novel methods are frequently evaluated against classical baselines (e.g., Spherical Splines) executed using their default software configurations, rather than being rigorously tuned for the specific dataset at hand. Furthermore, evaluations are often restricted to a single dataset or masking protocol, obscuring whether an algorithm is universally robust or merely overfitted to a specific experimental setup. 

The present work addresses this gap directly. Rather than proposing a new interpolation theory, we introduce a comprehensive, multi-dataset benchmarking pipeline powered by systematic hyperparameter optimization (via Optuna). This ensures that classical baselines and advanced temporal-GSP methods are compared at their absolute theoretical ceilings under diverse, realistic masking conditions.
