\section{Results}

The B3/B4 closure consolidated the B2 full-scale benchmark into publication-grade artefacts with explicit traceability. The quantitative claims in this section are anchored to REP-01 and STAT-02 outputs, while iterative evidence from it02-it130 is used only under the GO/NO-GO policy.

\subsection{Family-Level Summary (REP-01)}

Table~\ref{tab:b3_rep01_summary} summarizes the family-level aggregate over shared dataset, scenario, missing-ratio, graph, and seed contexts. A performance crossover is observed: Baseline achieves the lowest mean MAE (\ResBaselineMAEFull) and RMSE (\ResBaselineRMSEFull), whereas TV/Time achieves the lowest mean DTW (\ResTVDTWFull). Therefore, no single family dominates all criteria.

\begin{table}[t]
\centering
\caption{REP-01 final summary from B3/B4 closure.}
\label{tab:b3_rep01_summary}
\resizebox{\columnwidth}{!}{\input{tables/b3_rep01_final_table.tex}}
\end{table}

This crossover has practical implications. For pointwise amplitude fidelity, baseline and graph-aware instant methods remain competitive. For temporal pattern preservation, TV/Time methods provide a consistent DTW advantage.

\subsection{Statistical Significance (STAT-02)}

Family-level Wilcoxon tests reject $H_0$ for TV/Time versus Instant on MAE ($p = $\StatFamilyMAEpval) and DTW ($p = $\StatFamilyDTWpval). At method level, TRSS versus BGSRP rejects $H_0$ ($p = $\StatTRSSBGSRPpval), while TRSS versus \texttt{gsmooth} fails to reject $H_0$ ($p = $\StatTRSSGSPpval). These results support family-level differences but also show limited separability among top methods by MAE alone.

\subsection{Scenario Dependence}

Per-scenario rankings in \url{results/b2_publication_topk_by_family_scenario.csv} show that method ordering changes with region and missing ratio (\ResMissingLevels). This sensitivity is expected because frontal, temporal-lateral, occipital, and central contexts induce different spatial-temporal correlation structures. Consequently, method selection should be scenario-aware rather than globally fixed.

\subsection{Iterative Evidence it02--it130 (GO/NO-GO Policy)}

The extended campaign reports 90 GO iterations in the range it02--it130, with complete artefact closure in phases 11--18 even when gates were not passed. Under the policy, GO iterations are confirmatory and NO-GO iterations are contextual only.

Confirmatory GO examples from the final closure block are: it124 (missing-pattern realistic v2, $p=0.0265$, TV gain $+43.5\%$) and it125 (temporal-window sensitivity, $p=0.0232$, TV gain $+41.3\%$). In contrast, key NO-GO contextual results include it120 (controlled operational-close profile, $p=0.0535$) and it130 (final decision matrix, $p=0.1489$, recommendation \texttt{CONDICIONAL}). These NO-GO outputs inform limits and deployment risk, but are not used as confirmatory evidence.

\subsection{INS-13 Status (Mandatory)}

BGSRP is reported as \texttt{proxy\_or\_partial} with \texttt{strict\_close=False}. The strict 1:1 MATLAB/GSPBox closure remains open according to \url{results/ins13_strict_status.md}. Therefore, BGSRP claims are limited to controlled Python proxy validation and must not be interpreted as strict cross-stack equivalence.

\subsection{Traceability Block}

\begin{itemize}
\item \textbf{Claim}: Baseline leads MAE/RMSE (0.0713/0.1622). \textbf{Artefact}: \url{results/b3_rep01_final_table_overall.csv}. \textbf{Script}: \url{experiments/finalize_b3_b4.py}. \textbf{Tag}: B3/B4.
\item \textbf{Claim}: TV/Time leads DTW (0.4918). \textbf{Artefact}: \url{results/b3_rep01_final_table_overall.csv}. \textbf{Script}: \url{experiments/finalize_b3_b4.py}. \textbf{Tag}: B3/B4.
\item \textbf{Claim}: Family significance on MAE/DTW (reject $H_0$). \textbf{Artefact}: \url{results/b3_stat02_significance.csv}. \textbf{Script}: \url{experiments/finalize_b3_b4.py}. \textbf{Tag}: STAT-02.
\item \textbf{Claim}: INS-13 status proxy\_or\_partial with strict\_close=False. \textbf{Artefact}: \url{results/ins13_strict_status.md}. \textbf{Script}: \url{experiments/ins13_strict_matlab_compare.py}. \textbf{Tag}: INS-13.
\item \textbf{Claim}: Final matrix reports \texttt{CONDICIONAL} recommendation (it130, NO-GO). \textbf{Artefact}: \url{results/it130_final_decision_matrix_decision_matrix.csv}. \textbf{Script}: \url{experiments/run_future_work_it121_it130.py}. \textbf{Tag}: it130.
\end{itemize}
